### 2021-05-17 response.tex

\begin{mdframed}
\ldots\,Caption: The captions to some of the figures could be improved.

Fig 2: This caption starts with the word ‘additionally’ which doesn’t sit well.
Also the caption is too short, given that this is probably one of the more important figures.
It took me a while to realize what the terms ASM, CSM etc meant (They were in Table 2).
I would spell out these abbreviations (ASM, CSM, VSM, BSM) in the caption (Table 2 can remain unchanged), this will save the reader for having to search for their meaning.
The caption would also add one sentence on how to read the figure.
I know that earlier on the authors explain what an arrow means but that was some pages away and since plos comp bio are generally no computer scientists I would add that explanation of the arrow to the caption as well.

Fig 3: In general, notation used in UML diagrams is not familiar to most modelers but in this case the diagram looks simple enough that its seems fairly self-explanatory. No action required. \ldots
\end{mdframed}

We have adapted and extended the Fig 2 caption and added the abbreviations (BSM, QM, \dots) to the legend of the figure (instead of the caption).
We hope that this makes the content of the figure clearer to the reader.

@@

\begin{mdframed}
\ldots\,Software: As it stands it is likely that very few people will use WebProv, the reason is that it requires far too much work to install, plus does it also require a backend sever?

The tool looks useful so why make it difficult to get hold of?

What I would recommend is move everything if possible to the client (including the database which doesn’t seem large) and host it as a github web page project so that when a user clicks on the url the application will show up, no installation necessary (which I think is one of the main attractions of web software) – see https://pages.github.com/. I strongly recommend something like this otherwise your work will not have the impact it should. \ldots
\end{mdframed}

We were initially using GitHub Pages to deploy the first version of the software. We decided to switch to Netlify though since it offers better web hosting services.
In addition to deploying the frontend to Netlify, the backend and database are now deployed on cloud servers which should make it easier for readers of the publication to get an impression of the tool and the provenance information of the Wnt models.
It can be accessed now at \url{https://webprov.netlify.com}.
Due to funding restriction, we plan to shutdown this service by the end of the year.
It should still be relatively easy to install the app locally by following the README (see next paragraph).

@@

\begin{mdframed}
\ldots\,Minor:
1. Introduction, second paragraph, first sentence, ‘conduction’, is that the right word? \ldots
\end{mdframed}

We have changed the wording.

\begin{mdframed}
\ldots\, 2. There is no reference to the youtube video on page 4 (footnote 2), also put the github ural there as well since the github repository is mentioned.
\end{mdframed}

For most URLs, we have used hyperlinks.
Thus, clicking on \href{https://youtu.be/UzwHtptkYOU}{YouTube} in the former footnote 2 should have led you to the website \url{https://youtu.be/UzwHtptkYOU}.
We will make this video publicly available if the manuscript has been accepted for publication in PLOS Computation Biology.

@@

\begin{mdframed}
\ldots\, I suggest the entire manuscript is thoroughly proof-read as some of the grammar and word choices are a bit unusual. "cell biological systems" in the abstract is one example that could be tidied up. \ldots
\end{mdframed}

We have proofread the manuscript and corrected all mistakes.
We hope all language problems have been eliminated.

\begin{mdframed}
\ldots\, As the authors state, the knowledge they have extracted from the literature and encoded in the example provenance graph used in this work makes a useful contribution to the community of potential users of these Wnt signally models.
I wonder if the authors have any plans or thoughts on the integration of this knowledge into a community repository, perhaps in a way that others could contribute to?
For the subset of models that are available in the Biomodels database, for example, could the provenance knowledge be contributed back to the database? \ldots
\end{mdframed}

As we have stated in our conclusion, we think that accessible provenance information would be a valuable extension of the BioModels (or any other simulation model) repository.
Right now, comparing the entries of BioModels to our approach, the database contains provenance (meta-)information of type Simulation Model and may additionally contain information of type Simulation Experiment and Simulation Data.
The latter two usually comprise an experiment specification file, for instance a SED-ML file, as well as a figure showing the simulated data.
In our case, the following BioModels entries contain information about the simulation experiments: the entry for Lee et al. (2003)~\cite{Lee2003} contains both a SED-ML (and COPASI) file to reproduce parts of Fig 6 of that publication (corresponding to our SD6) and the entry for Padala et al. (2017)~\cite{Padala2017}contains the COPASI file to reproduce Fig 2A-C of that publication (corresponding to our SD3).
The overview of a model entry might also include information about Research Questions and Assumptions.
The other entities/activities and, more importantly, most relations are not available.

@@

When comparing this qualifier with our approach, we find that whenever we have a connection of the kind `Building Simulation Model (of simulation study \textit{i}) $\longrightarrow$ Simulation Model (of simulation study \textit{j})', we could add `model \textit{i} \textit{isDerivedFrom} model \textit{j}' to BioModels (see Figure~\ref{fig:KimDerived}).

As we have stated in our manuscript, \enquote{we have (...) not included the direct connection between two activities or two entities, such as the possibility to have a model being derived from another model. Thus, we have not included (...)  \texttt{WasDerivedFrom}, which describes a direct transformation (update) of an entity into a new one}.

Out of six Wnt models included in BioModels, two comprise information about model relations.
First, the model by Kim et al. (2007) has \textit{isDerivedFrom} information: `DOI 10.1007/3-540-36481-1\_11' (Cho et al. 2003) and `PubMed 1455190' (Lee et al. (2003)).
When comparing it with our provenance information, we have found an \textit{isDerivedFrom}-equivalent connection to Cho et al. (2003) and Cho et al. (2006).
The latter is missing in BioModels.
Cho et al. (2006), on the other hand, is connected to Lee et al. (2003).
(See our \href{https://github.com/SFB-ELAINE/SI_Provenance_Wnt_Family/tree/main/ProvenanceInformation}{GitHub repository} with additional files.
This link has also been given in the main text.)

Second, the model by Padala et al. (2017) contains the following \textit{isDerivedFrom} information: `BIOMD0000000623' (Orton et al. (2009)), `BIOMD0000000033' (Brown et al. (2004)), and `BIOMD0000000149' (Kim et al. (2007)).
All of these connections are also included in our provenance graph.
